---
title: "Task3 - Prediction using Decision Trees"
author: "Vishal Kumar"
date: "10/18/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

### Importing required libraries and dataset
We cannot import OneR and RWeka packages continously as 
OneR function in OneR package will masked by RWeka.
```{r}
library(OneR)
#library(RWeka)
library(rpart)
library(rpart.plot)
df <- iris
```

### Analyzing and checking our data
```{r}
head(df)
str(df)
```

### Using our first decision tree algorithm from OneR package
OneR algorithm takes into account only ONE most feature for RULE generation

```{r}
iris_1R <- OneR(Species ~ ., data = df)
iris_1R
```

We see the OneR algorithm has an accuracy of 94%

### Comparing our predicted values with Actual values with help of confusion matrix and exploring our model with graph
```{r}
iris_1R_pred <- predict(iris_1R, df)
table(actual = df$Species, predicted = iris_1R_pred)
plot(iris_1R)
```

### Improving performance with more robust models
### We now load our RWeka package and use the "JRip" algorithm
```{r}
library(RWeka)
iris_classifier <- JRip(Species ~ ., data = df)
iris_classifier
summary(iris_classifier)
```

### As we can now see We have an accuracy of 97%



### Using one more model from RWeka package to see if we can improve the performance
```{r, fig.width=20, fig.height=12}
library(partykit)
m1 <- J48(Species~. , data = df)
m1
plot(m1)

```


### The task is complete but explored more libraries for better results and easier implementation
### The rpart library provides the easiest way to make a decision tree.
```{r}
tree <- rpart(Species ~ ., data = df, cp=.02)
tree
summary(tree)
rpart.plot(tree, type=1, extra=1)
rpart.plot(tree, main="extra = 3,  under = TRUE", extra=3, under=TRUE, faclen=0)
```

## To sum up all the graphs and rules
```{r}
prp(tree)
```

