---
title: "Task 2"
author: "Vishal Kumar"
date: "13/10/2020"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
 
### Importing the required libraries
#### (No need to import iris dataset as it is already present in R package)
#### Also removing duplicated datas (if any).
```{r}
library(stats)
library(ggpubr)
library(factoextra) # clustering algorithms & visualization

dSet <- iris
dSet <- dSet[!duplicated(dSet),]
summary(dSet)
str(dSet)
```

### Preparing the data by removing the  SPECIES coloumn
#### # Plotting the results onto a line graph, allowing us to observe 'The elbow'
```{r}
dSet <- dSet[-5]
set.seed(100)
fviz_nbclust(dSet, kmeans, method = "wss")
```

### Applying kmeans clustering algorithm
```{r}

myclusters <- kmeans(iris[,-5], 3)
myclusters
```

### Plotting the cluster plot
```{r}
fviz_cluster(myclusters, data = iris[,-5], geom = "point")
```
### Using ggpubr package to get better view of the plot
```{r}
res.pca <- prcomp(iris[,-5],  scale = TRUE)
ind.coord <- as.data.frame(get_pca_ind(res.pca)$coord)
ind.coord$cluster <- factor(myclusters$cluster)
ind.coord$Species <- iris$Species
head(ind.coord)

eigenvalue <- round(get_eigenvalue(res.pca), 1)
variance.percent <- eigenvalue$variance.percent
head(eigenvalue)

ggscatter(
  ind.coord, x = "Dim.1", y = "Dim.2", 
  color = "cluster", palette = "npg", ellipse = TRUE, ellipse.type = "convex",
  shape = "Species", size = 1.5,  legend = "right", ggtheme = theme_bw(),
  xlab = paste0("Dim 1 (", variance.percent[1], "% )" ),
  ylab = paste0("Dim 2 (", variance.percent[2], "% )" )
) +
  stat_mean(aes(color = cluster), size = 4)
```

