---
title: "TASK 1"
author: "Vishal Kumar"
date: "11/10/2020"
output: html_document
---

### Importing the required libraries

```{r}
library(psych)
library(stats)
library(ggplot2)
library(Metrics)
```


### Importing the dataset
```{r}
timeTable <- read.csv("/home/vishal/GRIP/task1/student_scores - student_scores.csv")
str(timeTable)
```
```{r}
summary(timeTable)
```

```{r}
hist(timeTable$Hours)
```
From the bove histogram we could see, most of the people studied an average of 3 hours,

```{r}
f <- ggplot(timeTable, aes(Hours, Scores))
f + geom_jitter(size = 2) + ggtitle("Hours vs Percentage")
f + geom_smooth(size = 2)
```


```{r}
cor(timeTable[c("Hours", "Scores")])
pairs(timeTable[c("Hours", "Scores")])
pairs.panels(timeTable[c("Hours", "Scores")])
```

The oval-shaped object on each scatter plot is a correlation ellipse.
It provides a visualization of correlation strength. The more the
ellipse is stretched, the stronger the correlation.


### Training the model

```{r}
model <- lm(Scores ~ Hours, data = timeTable)
model
```

```{r}
summary(model)
```


```{r}
plot(timeTable$Hours, timeTable$Scores)
#abline(2.484, 9.776)
abline(lm(timeTable$Scores ~ timeTable$Hours))
```

### Predicting the score for Hour = 9.25
```{r}
predict_ans <- predict(model, data.frame(Hours = 9.25, Scores = ""))
print(predict_ans)
```
### Evaluating MODEL 1
We use Mean Absolute Error
```{r}
#pred <- predict(model, timeTable$Hours)
timeTable$Predicted <- predict(model, timeTable)
mae(timeTable$Scores, timeTable$Predicted)
```

## Refining The model

```{r}
timeTable$Hours2 <- timeTable$Hours^2
```


```{r}
model2 <- lm(Scores ~ Hours + Hours2, timeTable)
summary(model2)
```

### Predicting the score for Hour = 9.25
```{r}
predict_ans2 <- predict(model2, data.frame(Hours = 9.25, Hours2 = 9.25^2, Scores = ""))
predict_ans2
```

```{r}
plot(timeTable$Hours, timeTable$Scores)
#abline(2.484, 9.776)
abline(lm(timeTable$Scores ~ timeTable$Hours+timeTable$Hours2))
```

### Evaluating MODEL 2
We use Mean Absolute Error
```{r}
timeTable$Predicted2 <- predict(model2, timeTable)
mae(timeTable$Scores, timeTable$Predicted2)
```

